Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-17 paper.tex
Remove hyphen from 'open source'

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, implemented as part of the
open-source turbine design software QBlade. Simulations were run with the
default settings and zero Mach number, for the approximate average blade chord
Reynolds numbers encountered in the experiments.

>>>>

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, implemented as part of the
open source turbine design software QBlade. Simulations were run with the
default settings and zero Mach number, for the approximate average blade chord
Reynolds numbers encountered in the experiments.
